---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Travis build status](https://travis-ci.org/USCCANA/socnet.svg?branch=master)](https://travis-ci.org/USCCANA/socnet)
 [![Coverage status](https://codecov.io/gh/USCCANA/socnet/branch/master/graph/badge.svg)](https://codecov.io/github/USCCANA/socnet?branch=master)

# socnet

This R package is created to access the data available in the
SOCNET website https://lists.ufl.edu/cgi-bin/wa?A0=SOCNET, which is hosted
by The University of Florida in its Listserv website.

## Installation

This package is currently under develoment and is only available by downloading the bleeding edge version. You can use `devtools` to get it:

```r
devtools::install_github("USCCANA/socnet")
```


## Example

Before starts, let's first load the package.

```{r}
library(socnet)
```

Suppose that you want to look at the SOCNET archives, but you don't know from where to start. You can use the function `socnet_list_archives` to get a list of the archives that are available in the Listserv. 

```{r example-archives}
# Getting the URLs to the archives per month
archives <- socnet_list_archives(cached = TRUE)
head(archives)
```

Now that we have the list of archives, we can access one of them and list what are the subjects (emails) that show under that archive with the `socnet_list_subjects` function.

```{r example-subjects}
# What was discussed during Oct 17?: Getting the subjects during that time
subjects <- socnet_list_subjects(archives$url[1], cached = TRUE)
```

Let's take a look at the output

```{r}
str(subjects)
head(subjects[,-1])
```

Now, we can use the function `socnet_parse_subject` to actually get the data of a particular subject. Let's try with the subject titled ``r subjects$subject[1]``

```{r example-fetch-subject}
socnet_parse_subject(subjects$url[1])
```

As you can see, the function returned a list with two elements, a vector of meta information, and the actual email.

# Most active user (compose side)

```{r}
rankfun <- function(x, colnames, maxn = 50) {
  x <- as.data.frame(table(x))
  x <- x[order(-x$Freq),]
  dimnames(x) <- list(1:nrow(x), colnames)
  knitr::kable(x[1:maxn,], row.names = TRUE)  
}

# Getting the from column and removing weird characters
data("subjects")
from <- subjects$from
from <- iconv(from, to="ASCII//TRANSLIT")

# Removing <[log in to unmask]> message
from <- gsub("[<].+", "", from)

# Creating the table
rankfun(from, colnames=c("User", "Count"))
```


# Latest version of the cache data

```{r, results='asis', echo=FALSE}
readLines("inst/cache/readme.md", warn = FALSE)
```

